---
title: "Site Validation"
author: "Tina Cheng"
date: "3/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

# INSTRUCTIONS: Install packages

```{r}
install.packages("boxr", "tidyverse", "tidyxl")
```


```{r}
library(boxr)
library(tidyverse)
library(tidyxl)
```

# Data Query 

In data query, search for keyword "site"
Filtered with this "tag"
Copy data url 

```{r}
dir <- "paste url here"

#example:
dir <- "/Users/tcheng/Box Sync/WNS Data Vault/Pd Continental/data/raw_data/all_site.csv"
```


#Get authenticated in R

If you run this site validation, you need to get a client_id and client_secret from IT admin.

```{r}
box_auth(client_id = "", client_secret = "")
```


# Read in files

```{r}
readFUN <- function(file_type, xlsx_sheets, dir) {
  if(file_type == "csv") {
    dat <- read_csv(dir)
  }
  else if(file_type == "xlsx") {
    dat <- xlsx_cells(path = dir, sheets = xlsx_sheets)
  }
}

test_readFUN <- function() {
  dat <- readFUN("csv", dir = dir)
  #is returned dataframe a dataframe
  nrow(dat) > 0
}

```

# Verify column names

write 2 functions
1- function
2- test that function
assert if T/F - would throw an error
R unit test
extract transform load (ETL)


```{r}
sitename_colnames <- c("site_name", "site_id")
country_colnames c("country")
admin1_colnames <- c("admin1", "state", "province") #others???
admin2_colnames <- c("admin2", "county") #others???
latitude_colnames <- c("latitude", "Latitude", "Lat", "lat", "x")
longitude_colnames <- c("longitude", "Longitude", "long", "Long", "lng", "Y")
sitetype_colnames <- c("site_type")
sitematerial_colnames <- c("site_material")

# site column enforcement
verifycolnames <- function() {}

test_verifycolnames <- function() {}
```

functions are verbs, variables are nouns
tab complete - make names long and descriptive

# Verify each data type

```{r}
class(site_name) = c("character", "factor")
class(latitude) = "numeric"
class(longitude) = "numeric"
class(site_type) = c("character", "factor")
class(site_material) = c("character", "factor")
```

# For categorical fields, verify categories

```{r}
site_types <- c("cave", "mine", "tunnel", "adit", "bridge", "culvert", "building")
site_materials <- c("limestone", "graphite", "gypsum", "manmade - concrete") #others???
```

# Verify site location

```{r}
datC <- dat %>% 
  #check lat long - domain check
  mutate(latitude within -180 to 180) %>% 
  mutate(country_fromlatlong = map.where("world", .$longitude, .$latitude),
         country_check = tolower(country) = tolower(country_fromlatlong))
```

# Map

```{r}


```

